A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-03-20 paper/paper.tex
More comments

Our construction involves several details, some of them being visible only in the Coq formalization. A description at an informal level which we estimate to be however mathematically precise enough can be found in Sections~\ref{sec:ett} and~\ref{sec:itt}, while technical issues with the mechanization are explained in~\ref{sec:mech}.

The whole definition is highly dependent, with dependencies in
inequality proofs and in coherence conditions. In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we
give a definition in Extensional Type Theory, which roughly
corresponds to a level of reasoning ``à la set theory'' where coherence
conditions are thought as ``holding on the nose'' without having to
mention them explicitly once they are justified. In Section~\ref{sec:itt} and Tables~\ref{fulltab:coind}, \ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces}, \ref{fulltab:coh}, we
give a definition in Intentional Type Theory, where transporting along
the coherence conditions is made explicit. This makes the definition
more involved, but at the same time helps to understand the
specificities of coherence conditions.

>>>>

Our construction is highly dependent, with dependencies in inequality
and equality proofs. It involves several involved details, some of
them being visible only in the Coq formalization.

In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core},
\ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal,
mathematical definition in Extensional Type Theory, which roughly
corresponds to a level of reasoning ``à la set theory'' where
equalities are thought as ``holding on the nose'' without having to
mention them explicitly once they are justified. In
Section~\ref{sec:itt} and Tables~\ref{fulltab:coind},
\ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces},
\ref{fulltab:coh}, we give the same mathematical definition in
Intensional Type Theory, where transporting along coherence conditions
is now made explicit. Adding this level of details helps to understand
the specificities of coherence conditions.
